SAT Competition 2020\tnoteref{title}

### 2021-02-02 paper/main.tex
removed redundant tables

Kochemazov et al. improved three-tier clause-management by persisting
additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} in SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}. 
As can be seen in Table~\ref{tab:solvers-incremental}, numerous submissions to SAT Competition~2020 are forks of some recently award winning descendants of \solver{Maple}-based solver.

@@

\subsection{Sequential SAT Solving}
\label{sec:part:seq}

Sequential SAT solvers have been evaluated in the Main, Planning and Incremental Library track of SAT Competition~2020. 
A total of $18$ teams submitted correct solvers to the Main track of the competition. 
Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
The recent genealogy of all submissions is highlighted by \emph{base solver} and \emph{variant} columns. 
Underlined text is used to point out the important parts of the respective submissions name.

\begin{table}[h!]
\setlength\tabcolsep{4.5pt}%default: 6pt
%\renewcommand{\arraystretch}{1.03}%default: 1
\smaller
\centering
\begin{tabularx}{\linewidth}{Xllcccc}
\bf Team & \bf Base Solver & \bf Variant / Name & \bf M & \bf U & \bf S & \bf P \\
\hline
\arrayrulecolor{lightgray}

\multirow{3}{*}{Biere} & \multirow{3}{*}{\solbert{Kissat}} &  -- & 1 & 1 & -- & --\\
 &  &  \solver{sat} & 1 & 1 & 2 & --\\
 &  &  \solver{unsat} & -- & 1 & -- & 3\\
\hline
 Biere, Fleury &  \solver{Cadical} & \solbert{SC2020} & -- & -- & -- & --\\
\hline

\multirow{2}{*}{Zhang, Cai}
    & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Relaxed} & -- & -- & -- & --\\
% &  & \solver{Rel. noTimeParam} & \\
 &  & \solver{Rel. newTech} & 2 & -- & 1 & --\\
\hline

\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
 &  \multirow{2}{*}{\solver{CryptoMiniSat-CCAnr}} &  -- & 3 & -- & 3 & 2\\
 &  &  \solver{lsids} & 3 & -- & 3 & 2\\
\hline

\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solver{CryptoMiniSat-WalkSAT} & -- & -- & -- & -- & --\\
\hline

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 &  &  \solver{trail} & -- & 2 & -- & --\\
 &  &  \solver{alluip} & -- & 2 & -- & 1\\
 & \multirow{-3}{*}{\solver{CaDiCaL}} &  \solbert{alluip-trail} & -- & 2 & -- & 1\\
 \cline{2-7}
 & \solver{MapleLCMDist} & \solver{alluip-trail} & -- & -- & -- & -- \\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solver{MapleLCMDistCBT}} & \solbert{f2trc} & -- & 3 & -- & --\\
 & & \solver{f2trc-s} & -- & 3 & -- & --\\
 \cline{2-7}
 & \solver{MapleLCMDistCBT-DL} & \solver{f2trc} & -- & 3 & -- & --\\
\hline

\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solbert{MapleLCMDistCBT-DL-v3} & -- & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
 & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v3}} & \solbert{Undominated} & -- & -- & -- & -- \\
 &  & \solver{Undom. Top16} & -- & -- & -- & -- \\
 &  & \solver{Undom. Top24} & -- & -- & -- & -- \\
 &  & \solver{Undom. Top36} & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{\solbert{Ex}\solver{MapleLCMDistCBT}} & \solver{padc\_dl} & -- & -- & -- & -- \\
 &  & \solver{padc\_dl\_ovau\_lin} & -- & -- & -- & -- \\
 &  & \solver{padc\_dl\_ovau\_exp} & -- & -- & -- & -- \\
 &  & \solver{psids\_dl} & -- & -- & -- & -- \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & \solver{MapleLCMDistCBT-DL-v3} & \solbert{DurianSat} & -- & -- & -- & -- \\
\hline

\multirow{2}{*}{Chen}
 & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Maple\_Mix} & -- & -- & -- & -- \\
 &  & \solbert{Maple\_Simp} & -- & -- & -- & -- \\
\hline

Riveros & \solver{MapleLCMDistCBT} & \solbert{SLIME} & -- & -- & -- & -- \\
\hline

\multirow{3}{*}{Li, Wu, Xu, Chen}
 & \multirow{3}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Scavel} & -- & -- & -- & -- \\
 &  & \solver{Scavel01} & -- & -- & -- & -- \\
 &  & \solver{Scavel02} & -- & -- & -- & -- \\
\hline

\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
 & \multirow{2}{*}{\solbert{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & -- & -- & -- & -- \\
 &  & \solver{init} & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
 & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v2.2}} & \solbert{exp}\solver{-V-LGB} & -- & -- & -- & -- \\
 &  & \solver{exp-V-L} & -- & -- & -- & -- \\
 &  & \solver{exp-L} & -- & -- & -- & -- \\
 &  & \solver{exp-V} & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{4}{*}{\solbert{MapleCM}} & \solbert{+dist} & -- & -- & -- & -- \\
 &  & \solver{+dist+sattime2s+-} & -- & -- & -- & -- \\
 &  & \solver{+dist+simp2--} & -- & -- & -- & -- \\
 &  & \solver{used+dist} & -- & -- & -- & -- \\
\hline

Kaiser, Hartung & \solver{MapleLCMDist} & \solbert{PauSat} & -- & -- & -- & -- \\
\hline

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{\solbert{ParaFROST}} & -- & -- & -- & -- & -- \\
 &  & \solver{CBT} & -- & -- & -- & -- 
\end{tabularx}
\caption[Teams and Solvers in the Main Tracks]{\emph{Teams} and \emph{Solvers} in the Main Tracks. \emph{Base Solver} highlights solver genealogy while \emph{Variant} displays names of configurations and forks. Distinctive names are \solbert{underlined}. The rightmost columns indicate the awards given in the Main (\emph{M}) and Planning track (\emph{P}), and for performance on unsatisfiable (\emph{U}) and satisfiable (\emph{S}) instances.}
\label{tab:solvers-main}
\end{table}

@@

Four submissions made it to participate in the Incremental Library track, some of which, e.g, \solver{CryptoMiniSat-5}, have also been evaluated and awarded in the Main track. 
Submissions to the Incremental Library track have been evaluated with respect to $6$ different applications -- each with $50$ benchmark instances. 
Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers. 
In this table, \emph{Score} denotes the number of application categories in which the solvers won based on their PAR-2 score.

\begin{table}[ht]
\centering\small
\begin{tabular}{llc}
\bf Team & \bf Solver & \bf Place\\
\hline
Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 1 \\
Biere, Fleury & \solver{CaDiCaL 2020} & -- \\
Chen & \solver{abcdsat-i20} & -- \\
Manthey & \solver{Riss 7.1.2} & -- 
\end{tabular}
\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track.}
\label{tab:solvers-incremental}
\end{table}

@@

\solver{Kissat} is a low-level re-implementation of \solver{CaDiCaL} with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}. 
Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}.

Since conflict-rate has been observed to be too unstable for the use-case, \solver{Kissat} uses the new unit ``ticks'', which is based on the approximate number of cache-line accesses, to measure the length of two alternating restart-modes~\cite{Biere:SC2020}.

@@

\subsection{Parallel SAT Solving: Winners of the Parallel Track}
\label{sec:part:par}

\begin{table}[b]
\centering\small
\begin{tabular}{llccc}
\bf Team & \bf Solver & \bf U+S & \bf U & \bf S \\
\hline\arrayrulecolor{lightgray}
\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
 & \solver{Painless-MCOMSPS-STR-32} & 1 & 2 & 1 \\
 & \solver{Painless-MCOMSPS-STR-64} & 1 & --& --\\
\hline
\multirow{2}{*}{Biere, Fazekas, Heisinger}
 & \solver{Plingeling} & 2 & 1 & 3 \\
 & \solver{Treengeling} & --& --& --\\
\hline
\multirow{2}{*}{Nabeshima, Inoue}
 & \solver{ManyGlucose-32} & 3 & 3 & -- \\
 & \solver{ManyGlucose-64} & -- & 3 & --\\
\hline
\multirow{2}{*}{Tchinda, Djamegni}
 & \solver{Painless-Maple-v1} & --& --& 2 \\
 & \solver{Painless-Maple-v2} & --& --& 2 \\
\hline
Li, Wu, Xu, Chen & \solver{Syrup Scavel} & --& --& --\\
%\hline
Chen & \solver{abcdSAT-p20} & --& --& --
\end{tabular}
\caption{Teams and Solvers participating in the Parallel track.}
\end{table}

@@

\subsection{Massively Parallel SAT Solving: Winners of the Cloud Track}
\label{sec:part:cloud}

\begin{table}[t]
\centering\small
\begin{tabular}{llc}
\bf Team & \bf Solver & \bf Place\\
\hline\arrayrulecolor{lightgray}
Schreiber & \solver{Mallob Mono} & 1\\
Ehlers, Kulczynski, Nowotka, Sieweck & \solver{TopoSAT 2} & 2\\
Riveros & \solver{Slime} & 3\\
\hline
\multirow{2}{*}{Biere, Fazekas, Fleury, Heisinger} & \solver{Paracooba}, & --\\
& \solver{Paracooba-March} & --\\
\hline
Hartung & \solver{CTSat} & --
\end{tabular}
\caption{Teams and solvers participating in the Cloud track.}
\end{table}

>>>>

Kochemazov et al. improved three-tier clause-management by persisting
additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} in SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}. 
As can be seen in Table~\ref{tab:solvers-main}, numerous submissions to SAT Competition~2020 are forks of some recently award winning descendants of \solver{Maple}-based solver.

@@

\subsection{Sequential SAT Solvers}
\label{sec:part:seq}

Sequential SAT solvers have been evaluated in the Main, Planning and Incremental Library track of SAT Competition~2020. 
$18$ teams submitted a total of $48$ solvers and configurations to the Main track and the Planning track of the competition, and $4$ solvers participated the Incremental Library track. 
%and were ranked by the number of application categories in which they won based on their PAR-2 score. 
%Submissions to the Incremental Library track have been evaluated with respect to $6$ different applications -- each with $50$ benchmark instances. 
%
Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
In the following sections, we outline the technical reports of the award winning solvers.

\begin{table}[h!]
\setlength\tabcolsep{4.5pt}%default: 6pt
%\renewcommand{\arraystretch}{1.03}%default: 1
\smaller
\centering
\begin{tabularx}{\linewidth}{Xllccccc}
\bf Team & \bf Base Solver & \bf Variant Name & \bf M & \bf U & \bf S & \bf P & \bf I \\
\hline
\arrayrulecolor{lightgray}

\multirow{3}{*}{Biere} & \multirow{3}{*}{\solbert{Kissat}} &  -- & 1 & 1 & -- & -- & --\\
 &  &  \solver{sat} & 1 & 1 & 2 & -- & --\\
 &  &  \solver{unsat} & -- & 1 & -- & 3 & --\\
\hline
 Biere, Fleury &  \solver{Cadical} & \solbert{SC2020} & -- & -- & -- & -- & --\\
\hline

\multirow{2}{*}{Zhang, Cai}
    & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Relaxed} & -- & -- & -- & -- & --\\
% &  & \solver{Rel. noTimeParam} & \\
 &  & \solver{Rel. newTech} & 2 & -- & 1 & -- & --\\
\hline

\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
 &  \multirow{2}{*}{\solver{CryptoMiniSat-CCAnr}} &  -- & 3 & -- & 3 & 2 & 1 \\
 &  &  \solver{lsids} & 3 & -- & 3 & 2 & --\\
\hline

\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solver{CryptoMiniSat-WalkSAT} & -- & -- & -- & -- & -- & --\\
\hline

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 &  &  \solver{trail} & -- & 2 & -- & -- & --\\
 &  &  \solver{alluip} & -- & 2 & -- & 1 & --\\
 & \multirow{-3}{*}{\solver{CaDiCaL}} &  \solbert{alluip-trail} & -- & 2 & -- & 1 & --\\
 \cline{2-8}
 & \solver{MapleLCMDist} & \solver{alluip-trail} & -- & -- & -- & -- & -- \\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solver{MapleLCMDistCBT}} & \solbert{f2trc} & -- & 3 & -- & -- & --\\
 & & \solver{f2trc-s} & -- & 3 & -- & -- & --\\
 \cline{2-8}
 & \solver{MapleLCMDistCBT-DL} & \solver{f2trc} & -- & 3 & -- & -- & --\\
\hline

\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solbert{MapleLCMDistCBT-DL-v3} & -- & -- & -- & -- & --  & --\\
\hline

\multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
 & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v3}} & \solbert{Undominated} & -- & -- & -- & -- & --\\
 &  & \solver{Undom. Top16} & -- & -- & -- & -- & -- \\
 &  & \solver{Undom. Top24} & -- & -- & -- & -- & -- \\
 &  & \solver{Undom. Top36} & -- & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{\solbert{Ex}\solver{MapleLCMDistCBT}} & \solver{padc\_dl} & -- & -- & -- & -- & -- \\
 &  & \solver{padc\_dl\_ovau\_lin} & -- & -- & -- & -- & -- \\
 &  & \solver{padc\_dl\_ovau\_exp} & -- & -- & -- & -- & -- \\
 &  & \solver{psids\_dl} & -- & -- & -- & -- & -- \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & \solver{MapleLCMDistCBT-DL-v3} & \solbert{DurianSat} & -- & -- & -- & -- & -- \\
\hline

\multirow{2}{*}{Chen}
 & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Maple\_Mix} & -- & -- & -- & -- & -- \\
 &  & \solbert{Maple\_Simp} & -- & -- & -- & -- & -- \\
\hline

Riveros & \solver{MapleLCMDistCBT} & \solbert{SLIME} & -- & -- & -- & -- & -- \\
\hline

\multirow{3}{*}{Li, Wu, Xu, Chen}
 & \multirow{3}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Scavel} & -- & -- & -- & -- & -- \\
 &  & \solver{Scavel01} & -- & -- & -- & -- & -- \\
 &  & \solver{Scavel02} & -- & -- & -- & -- & -- \\
\hline

\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
 & \multirow{2}{*}{\solbert{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & -- & -- & -- & -- & -- \\
 &  & \solver{init} & -- & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
 & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v2.2}} & \solbert{exp}\solver{-V-LGB} & -- & -- & -- & -- & -- \\
 &  & \solver{exp-V-L} & -- & -- & -- & -- & -- \\
 &  & \solver{exp-L} & -- & -- & -- & -- & -- \\
 &  & \solver{exp-V} & -- & -- & -- & -- & -- \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{4}{*}{\solbert{MapleCM}} & \solbert{+dist} & -- & -- & -- & -- & -- \\
 &  & \solver{+dist+sat2s} & -- & -- & -- & -- & -- \\
 &  & \solver{+dist+simp2} & -- & -- & -- & -- & -- \\
 &  & \solver{used+dist} & -- & -- & -- & -- & -- \\
\hline

Kaiser, Hartung & \solver{MapleLCMDist} & \solbert{PauSat} & -- & -- & -- & -- & -- \\
\hline

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{\solbert{ParaFROST}} & -- & -- & -- & -- & -- & -- \\
 &  & \solver{CBT} & -- & -- & -- & -- & --
\end{tabularx}
\caption{\emph{Teams} and \emph{Solvers} in the Main, Planning and Incremental Library Track. Column \emph{Base Solver} highlights solver genealogy, and \emph{Variant Name} displays names of configurations and forks. Distinctive names are \solbert{underlined}. The rightmost columns indicate the awards given in the Main (\emph{M}) track, for performance on unsatisfiable (\emph{U}) and satisfiable (\emph{S}) instances, and in the Planning (\emph{P}) and Incremental Library (\emph{I}) track.}
\label{tab:solvers-main}
\end{table}

@@

%\begin{table}[ht]
%\centering\small
%\begin{tabular}{llc}
%\bf Team & \bf Solver & \bf Place\\
%\hline
%Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 1 \\
%Biere, Fleury & \solver{CaDiCaL 2020} & -- \\
%Chen & \solver{abcdsat-i20} & -- \\
%Manthey & \solver{Riss 7.1.2} & -- 
%\end{tabular}
%\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track.}
%\label{tab:solvers-incremental}
%\end{table}

@@

\solver{Kissat} is a low-level re-implementation of \solver{CaDiCaL} with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}. 
Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
Since conflict-rate has been observed to be too unstable for the use-case, \solver{Kissat} uses the new unit ``ticks'', which is based on the approximate number of cache-line accesses, to measure the length of two alternating restart-modes~\cite{Biere:SC2020}.

@@

\subsection{Parallel SAT Solvers}
\label{sec:part:par}

Six Teams submitted a total of $10$ solvers and configurations in the Parallel track. 
In the following, we outline the technical reports of the award winning parallel solvers.

%\begin{table}[b]
%\centering\small
%\begin{tabular}{llccc}
%\bf Team & \bf Solver & \bf U+S & \bf U & \bf S \\
%\hline\arrayrulecolor{lightgray}
%\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
% & \solver{Painless-MCOMSPS-STR-32} & 1 & 2 & 1 \\
% & \solver{Painless-MCOMSPS-STR-64} & 1 & --& --\\
%\hline
%\multirow{2}{*}{Biere, Fazekas, Heisinger}
% & \solver{Plingeling} & 2 & 1 & 3 \\
% & \solver{Treengeling} & --& --& --\\
%\hline
%\multirow{2}{*}{Nabeshima, Inoue}
% & \solver{ManyGlucose-32} & 3 & 3 & -- \\
% & \solver{ManyGlucose-64} & -- & 3 & --\\
%\hline
%\multirow{2}{*}{Tchinda, Djamegni}
% & \solver{Painless-Maple-v1} & --& --& 2 \\
% & \solver{Painless-Maple-v2} & --& --& 2 \\
%\hline
%Li, Wu, Xu, Chen & \solver{Syrup Scavel} & --& --& --\\
%\hline
%Chen & \solver{abcdSAT-p20} & --& --& --
%\end{tabular}
%\caption{Teams and Solvers participating in the Parallel track.}
%\end{table}

@@

\subsection{Massively Parallel SAT Solvers}
\label{sec:part:cloud}

Five teams submitted a total of $6$ solvers and configuration in the Cloud track. 
In the following, we outline the technical reports of the award winning massively parallel solvers.

%\begin{table}[t]
%\centering\small
%\begin{tabular}{llc}
%\bf Team & \bf Solver & \bf Place\\
%\hline\arrayrulecolor{lightgray}
%Schreiber & \solver{Mallob Mono} & 1\\
%Ehlers, Kulczynski, Nowotka, Sieweck & \solver{TopoSAT 2} & 2\\
%Riveros & \solver{Slime} & 3\\
%\hline
%\multirow{2}{*}{Biere, Fazekas, Fleury, Heisinger} & \solver{Paracooba}, & --\\
%& \solver{Paracooba-March} & --\\
%\hline
%Hartung & \solver{CTSat} & --
%\end{tabular}
%\caption{Teams and solvers participating in the Cloud track.}
%\end{table}
